---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(purrr)
```

## Loading the data

Each data file is read and added to a single data frame. 

```{r message=FALSE, warning=FALSE}
data.all <- NA
directory <- 'data/base_study'
data.files <- dir(directory, pattern=".txt")
warmup <- 0 # can throw out the first N samples, but we sorted out the problem that was necessitating this.
samples <- 200
for(f in data.files){
  vars <- str_split(f, "_|\\.")[[1]]
  data.this <- read_tsv(paste0(directory,"/", f)) %>% 
    select(c('Opto 3 Onset', 'Opto 3 Offset')) %>%
    mutate(method=vars[1], system = vars[2], browser=vars[3], duration=as.numeric(vars[4])) %>%
    slice((1+warmup):(warmup+samples))
  if(is.na(data.all)){
    data.all <- data.this
  } else {
    data.all <- rbind(data.all, data.this)
  }
}
```


We add columns that contain the duration of the stimulus as measured by the BBTK, a conversion of this duration to the number of frames that the stimulus was displayed, and the desired number of frames to display, and the error in the number of frames displayed.

```{r}
frame.rate <- 1000/60
data.all <- data.all %>% 
  mutate(obs.duration = `Opto 3 Offset` - `Opto 3 Onset`, 
         frames = round(obs.duration / frame.rate), 
         desired.frames = round(duration / frame.rate),
         frame.error = frames - desired.frames)
```


## Summary of error for each condition.

We calculate the number of presentations with particular frame errors (e.g., 1 frame too long, 1 frame too short) for each condition (method, browser, system combination).

```{r}
error.summary <- data.all %>% group_by(method, browser, system, desired.frames, frame.error) %>% summarize(count = n())

error.summary
```

In some cases the counts above are less than 200 trials per cell because the stimulus was never displayed so the BBTK did not record anything. We can recover those errors here.

```{r}
count.per.run <- error.summary %>% group_by(method, browser, system, desired.frames) %>% 
  summarize(count = sum(count)) %>% filter(count < samples) %>% mutate(missing.trials = samples - count) %>%
  mutate(frame.error = -desired.frames) %>% select(method, browser, system, desired.frames, frame.error, missing.trials) %>%
  rename(count = missing.trials)

# merge data back together
error.summary <- rbind(error.summary, count.per.run) %>% arrange(method, browser, system, desired.frames)
```

Now we can nest the data by system and browser to generate plots for each {browser, system} pair.

```{r}
plotting.function <- function(data){
  p <- ggplot(data, aes(x=frame.error, y=count, fill=method))+
        scale_fill_brewer(type="qual", palette = "Set1", name="Method")+
        geom_vline(xintercept = 0, color="grey50")+
        geom_bar(stat='identity') +
        labs(x="Error in displayed frame count", y="Count")+
        facet_grid(method ~ desired.frames)+
        theme_minimal()+
        theme(panel.grid=element_blank())
  return(p)
}

nested.error.summary <- error.summary %>% group_by(browser, system) %>% nest() %>% mutate(plot = map(data, plotting.function))
```

## Chrome, PC

```{r fig.height=12, fig.width=12}
(nested.error.summary %>% filter(system == 'pc', browser == 'chrome'))$plot[[1]]
```

## Chrome, Linux

```{r fig.height=12, fig.width=12}
(nested.error.summary %>% filter(system == 'linux', browser == 'chrome'))$plot[[1]]
```

## Firefox, PC

```{r fig.height=12, fig.width=12}
(nested.error.summary %>% filter(system == 'pc', browser == 'firefox'))$plot[[1]]
```

## Firefox, Linux

```{r fig.height=12, fig.width=12}
(nested.error.summary %>% filter(system == 'linux', browser == 'firefox'))$plot[[1]]
```

## Edge, PC

```{r fig.height=12, fig.width=12}
(nested.error.summary %>% filter(system == 'pc', browser == 'edge'))$plot[[1]]
```